Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-08-14 paper.qmd
Updated the Figure 10 labels

```{r}
#| label: plot-theme
theme_set(theme_linedraw() +
   theme(
     #aspect.ratio = 1,
     plot.background = element_rect(fill = 'transparent', colour = NA),
     plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
     panel.background = element_rect(fill = 'transparent', 
                                     colour = NA),
     panel.grid.major = element_blank(), 
     panel.grid.minor = element_blank(), 
     axis.title.x = element_blank(), axis.title.y = element_blank(),
     axis.text.x = element_blank(), axis.ticks.x = element_blank(),
     axis.text.y = element_blank(), axis.ticks.y = element_blank(),
     legend.background = element_rect(fill = 'transparent', 
                                      colour = NA),
     legend.key = element_rect(fill = 'transparent', 
                               colour = NA),
     legend.position = "bottom", 
     legend.title = element_blank(), 
     legend.text = element_text(size=4),
     legend.key.height = unit(0.25, 'cm'),
     legend.key.width = unit(0.25, 'cm')
   )
)
interior_annotation <- function(label, position = c(0.92, 0.92)) {
  annotation_custom(grid::textGrob(label = label,
      x = unit(position[1], "npc"), y = unit(position[2], "npc"),
      gp = grid::gpar(cex = 1, col="grey70")))
}
```

@@

five_gau_proj_tsne_model <- projected_df |>
  filter(type == "data") |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
      geom_point(
        alpha = 0.3) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#33a02c") +
  scale_color_manual(values = c("#000000", "#33a02c")) +
  xlim(c(-0.18, 0.1)) +
  ylim(c(-0.78, -0.55))

@@

five_gau_proj_umap_model <- projected_df |>
  filter(type == "data") |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
      geom_point(
        alpha = 0.3) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#33a02c") +
  scale_color_manual(values = c("#000000", "#33a02c")) +
  xlim(c(-0.18, 0.1)) +
  ylim(c(-0.78, -0.55))

@@

five_gau_proj_pacmap_model <- projected_df |>
  filter(type == "data") |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
      geom_point(
        alpha = 0.3) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#33a02c") +
  scale_color_manual(values = c("#000000", "#33a02c")) +
  xlim(c(-0.18, 0.1)) +
  ylim(c(-0.78, -0.55))

>>>>

```{r}
#| label: plot-theme
theme_set(theme_linedraw() +
   theme(
     #aspect.ratio = 1,
     plot.background = element_rect(fill = 'transparent', colour = NA),
     plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
     panel.background = element_rect(fill = 'transparent', 
                                     colour = NA),
     panel.grid.major = element_blank(), 
     panel.grid.minor = element_blank(), 
     axis.title.x = element_blank(), axis.title.y = element_blank(),
     axis.text.x = element_blank(), axis.ticks.x = element_blank(),
     axis.text.y = element_blank(), axis.ticks.y = element_blank(),
     legend.background = element_rect(fill = 'transparent', 
                                      colour = NA),
     legend.key = element_rect(fill = 'transparent', 
                               colour = NA),
     legend.position = "bottom", 
     legend.title = element_blank(), 
     legend.text = element_text(size=4),
     legend.key.height = unit(0.25, 'cm'),
     legend.key.width = unit(0.25, 'cm')
   )
)
interior_annotation <- function(label, position = c(0.92, 0.92), cex = 1) {
  annotation_custom(grid::textGrob(label = label,
      x = unit(position[1], "npc"), y = unit(position[2], "npc"),
      gp = grid::gpar(cex = cex, col="grey70")))
}
```

@@

five_gau_proj_tsne_model <- projected_df |>
  filter(type == "data") |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
      geom_point(
        alpha = 0.3) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#33a02c") +
  scale_color_manual(values = c("#000000", "#33a02c")) +
  xlim(c(-0.18, 0.1)) +
  ylim(c(-0.78, -0.55)) +
  interior_annotation("a", 
                      position = c(0.08, 0.9),
                      cex = 3)

@@

five_gau_proj_umap_model <- projected_df |>
  filter(type == "data") |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
      geom_point(
        alpha = 0.3) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#33a02c") +
  scale_color_manual(values = c("#000000", "#33a02c")) +
  xlim(c(-0.18, 0.1)) +
  ylim(c(-0.78, -0.55)) +
  interior_annotation("b", 
                      position = c(0.08, 0.9),
                      cex = 3)

@@

five_gau_proj_pacmap_model <- projected_df |>
  filter(type == "data") |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
      geom_point(
        alpha = 0.3) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#33a02c") +
  scale_color_manual(values = c("#000000", "#33a02c")) +
  xlim(c(-0.18, 0.1)) +
  ylim(c(-0.78, -0.55)) +
  interior_annotation("c", 
                      position = c(0.08, 0.9),
                      cex = 3)
